Enhancement of SDR in Thessaloniki

### 2024-03-12 GHI_enh_04_investigate.tex
Commit 2024-03-12 13:11

\begin{verbatim}
Warning: Continuous x aesthetic
i did you forget `aes(group = ...)`?
\end{verbatim}

@@

@@

\begin{verbatim}
2024-03-12 09:57:38.0 athan@tyler GHI_enh_04_investigate.R 1.109494 mins
\end{verbatim}

>>>>

\begin{verbatim}
Warning: The `fun.y` argument of `stat_summary()` is deprecated as of ggplot2 3.3.0.
i Please use the `fun` argument instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_ECE_month_norm_MAX_median_N-2} \end{center}

@@

\begin{verbatim}
2024-03-12 10:27:22.9 athan@tyler GHI_enh_04_investigate.R 1.200812 mins
\end{verbatim}
